Map of France with a grid

### 2024-08-22 All3_tables.Rmd
Cleaner map and cleaner tables

```{r}
tab_real <- real_df %>%
  kable("latex", booktabs = TRUE, align = "lccc", linesep = c("", "\\addlinespace", "", "", "", ""), 
        caption = paste("True values proper to the database"), col.names = gsub("[.]", " ", names(real_df))) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

@@

```{r}
tab_ci <- df_total %>%
  kable("latex", booktabs = TRUE, align = "llcccc", linesep = c("", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\hline"), caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

>>>>

```{r}
tab_real <- real_df %>%
  kable("latex", booktabs = FALSE, align = "lccc", linesep = c("", "\\addlinespace", "", "", "", ""), 
        caption = paste("True values proper to the database"), col.names = gsub("[.]", " ", names(real_df))) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

@@

```{r}
tab_ci <- df_total %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0, 16,32), hline_after = T) %>% 
  row_spec(c(16,32), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

### 2024-08-22 All_tables.Rmd
Cleaner map and cleaner tables

```{r}
B0 <- 1000
```

@@

```{r}
B1 <- 200
B2 <- 100
```

@@

```{r}
tab_ci <- df_total %>%
  kable("latex", booktabs = TRUE, align = "llcccc", linesep = c("", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\addlinespace", "", "", "", "\\hline"), caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

@@

```{r}
tab_var <- diff_var %>%
  kable("latex", booktabs = TRUE, align = "lc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste("Comparison of the two methods when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

>>>>

```{r}
B0 <- 10
```

@@

```{r}
B1 <- 10
B2 <- 10
```

@@

```{r}
tab_ci <- df_total %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications")) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0, 16,32), hline_after = T) %>% 
  row_spec(c(16,32), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r}
tab_var <- diff_var %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste("Comparison of the two methods when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  collapse_rows(columns = 1, latex_hline = "major")
```

### 2024-08-22 Map_FR.Rmd
Cleaner map and cleaner tables

---
title: "Map of France"
output: pdf_document
date: "2024-08-20"
---

@@

```{r}
library(ggplot2)
```

## Test

```{r}
map <- map_data("france")
ggplot(map)
```

# Another test

```{r}
install.packages("CARTElette")
library(CARTElette)
```

```{r}
shp_commune <- charger_carte(COG = 2019, nivsupra = "COM")
```

# No despair

```{r}
install.packages("sf")
install.packages("tmap")
```

```{r}
library(sf)
library(tmap)
```

```{r}
departements_l93 <- read_sf("~/work/Sim_article2024/DEPARTEMENT.shp")
```

# The cat

```{r}
# Installer les packages nécessaires si vous ne les avez pas déjà
install.packages(c("sf", "rnaturalearth", "ggplot2", "rnaturalearthdata"))

# Charger les packages
library(sf)
library(rnaturalearth)
library(ggplot2)
```

```{r}
# Télécharger les données du fond de carte
france_map <- ne_countries(scale = "medium", country = "France", returnclass = "sf")

# Afficher la carte de la France métropolitaine
ggplot(data = france_map) +
  geom_sf() +
  coord_sf(xlim = c(-6, 10), ylim = c(41, 52), expand = FALSE) +
  geom_tile(data = grid_data, aes(x = lon, y = lat, fill = color), alpha = 0.5) +
  theme_minimal() +
  labs(title = "Carte de la France Métropolitaine")

```

```{r}

# Télécharger les données du fond de carte
france_map <- ne_countries(scale = "medium", country = "France", returnclass = "sf")

# Définir les limites de la France métropolitaine pour la grille
xlims <- c(-6, 10)
ylims <- c(40, 52)

cell_width <- 1.0  # largeur des cases
cell_height <- 1.0  # hauteur des cases

# Créer une grille régulière de coordonnées
grid_data <- expand.grid(
  lon = seq(xlims[1], xlims[2], by = 0.1),  # Espacement horizontal
  lat = seq(ylims[1], ylims[2], by = 0.1)   # Espacement vertical
)

# Créer une colonne fictive pour colorier certaines cases
grid_data$color <- ifelse(grid_data$lon > 2 & grid_data$lon < 4 & 
                            grid_data$lat > 46 & grid_data$lat < 48, 
                          "highlight", "normal")

# Afficher la carte avec la grille par-dessus
ggplot(data = france_map) +
  geom_sf(fill = "white", color = "black") +
  coord_sf(xlim = xlims, ylim = ylims, expand = FALSE) +
  geom_tile(data = grid_data, aes(x = lon, y = lat, fill = color), alpha = 0.5) +
  scale_fill_manual(values = c("highlight" = "red", "normal" = "transparent")) +
  theme_minimal() +
  labs(title = "Carte de la France Métropolitaine avec une Grille")

```

```{r}
# Définir les limites de la France métropolitaine pour la grille
xlims <- c(-5, 10)
ylims <- c(41, 52)

# Définir la taille des cases de la grille
cell_width <- 1.0  # largeur des cases
cell_height <- 1.0  # hauteur des cases

# Créer une grille régulière de coordonnées
grid_data <- expand.grid(
  lon = seq(xlims[1], xlims[2], by = cell_width),  # Espacement horizontal
  lat = seq(ylims[1], ylims[2], by = cell_height)  # Espacement vertical
)

# Créer une colonne fictive pour colorier certaines cases (à modifier selon vos besoins)
grid_data$color <- ifelse(grid_data$lon > 2 & grid_data$lon < 4 & 
                            grid_data$lat > 46 & grid_data$lat < 48, 
                          "highlight", "normal")

# Afficher la carte avec la grille par-dessus
ggplot() +
  geom_sf(data = france_map, fill = "white", color = "black") +
  coord_sf(xlim = xlims, ylim = ylims, expand = FALSE) +
  geom_tile(data = grid_data, aes(x = lon, y = lat, fill = color), 
            width = cell_width, height = cell_height, alpha = 0.5) +
  scale_fill_manual(values = c("highlight" = "red", "normal" = "transparent")) +
  theme_minimal() +
  labs(title = "Carte de la France Métropolitaine avec une Grille")

```

>>>>

---
title: "Map of France with a grid"
output: pdf_document
date: "2024-08-21"
---

Goal: to produce a map of France with a grid and colored small squares

@@

```{r}
install.packages("ggplot2")
install.packages("sf")
install.packages("ggspatial")
```

```{r}
library(ggplot2)
library(sf)
library(ggspatial)
```

```{r}
install.packages("rnaturalearth")
install.packages("rnaturalearthdata")
library(rnaturalearth)
library(rnaturalearthdata)

# Get the map data for metropolitan France
france <- ne_countries(scale = "medium", country = "France", returnclass = "sf")
```

```{r}
# Create a data frame with the coordinates and colors
# grid_data <- expand.grid(x = 1:30, y = 1:30)  # 10x10 grid
# grid_data$color <- "white"  # Default color for all squares

# (10--5)*2 = 30
# (51.5-41)*2 = 21

# Function to sample at random following the grid
sampling_grid <- function(i){
  cells_x <- c()
  cells_y <- c()

  for (l in 0:20) {
    if (l==0){
      x_init <- i
    }else if ((3*l+i) < 10){
      x_init <- (3*l+i)
    }else{
      x_init <- (((3*l+i))%%(10))
    }
    k <- 0
    while (x_init + 10*k < 30) {
      a <- x_init + 10*k
      b <- l
      cells_x <- append(cells_x, a)
      # print(a)
      cells_y <- append(cells_y, b)
      # print(b)
      k <- k+1
    }
  }
  return(data.frame(x = cells_x, y = cells_y))
}

test <- sampling_grid(3)
```

```{r}
# Define grid parameters
xmin <- -5   # Westernmost longitude
xmax <- 10   # Easternmost longitude
ymin <- 41   # Southernmost latitude
ymax <- 51.5   # Northernmost latitude
grid_size <- 0.5  # Grid size in degrees

# Create a grid
grid <- expand.grid(
  x = seq(xmin, xmax, by = grid_size),
  y = seq(ymin, ymax, by = grid_size)
)

# Convert the grid to an sf object
grid_sf <- st_as_sf(grid, coords = c("x", "y"), crs = 4326)

# Convert grid points to grid cells (polygons)
grid_sf <- st_make_grid(grid_sf, cellsize = c(grid_size, grid_size))

# Highlight specific cells
highlighted_cells <- grid_sf[test$x + (test$y)*30, ]  # Example: highlight specific cells
highlighted_cells <- st_sf(geometry = highlighted_cells, color = "red")  # Assign color

# Combine highlighted and non-highlighted cells
grid_sf <- st_sf(geometry = grid_sf, color = "white")
grid_sf$color[which(grid_sf$geometry %in% highlighted_cells$geometry)] <- highlighted_cells$color
```

```{r}
### First step: all chosen small squares in the grid

# Plot the map
ggplot() +
  geom_sf(data = france, fill = "lightblue") +
  geom_sf(data = grid_sf, aes(fill = color), color = "black", alpha = 0.4) +
  scale_fill_identity() +  # Use the colors defined in the grid_sf object
  coord_sf(xlim = c(xmin, xmax), ylim = c(ymin, ymax)) +
  theme_minimal() +
  ggtitle("Firs-stage sampling: sampling of cells within a grid") 
# +
  # annotation_scale(location = "bl") + # location = NULL
  # annotation_north_arrow(location = "bl")
```

```{r}
# Intersect grid with the map of France
intersected <- st_intersection(grid_sf, france)

# Create a new column to determine land or water (or other features)
# Here, we'll simply mark if a grid cell intersects with land (France)
grid_sf$color2 <- ifelse(st_intersects(grid_sf, france, sparse = FALSE), "green", "blue")
```

```{r}
grid_sf$color3 <- ifelse((grid_sf$color2 == "green") & (grid_sf$color == "red"), "orange", "white")
```

```{r}
### Second step: all chosen small squares that have at least a land part

# Plot the map with color-coded grid cells
ggplot() +
  geom_sf(data = france, fill = "lightblue") +
  geom_sf(data = grid_sf, aes(fill = color3), color = "black", alpha = 0.4) +
  scale_fill_identity() +  # Use the colors defined in the grid_sf object
  coord_sf(xlim = c(xmin, xmax), ylim = c(ymin, ymax)) +
  theme_minimal() 
# +
  # ggtitle("")
```
